---
title: "BiocReporting tools"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{BiocReporting tools}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup,echo=FALSE,results="hide"}
suppressMessages({
suppressPackageStartupMessages({
library(BiocReporting)
options(scipen=10000)
library(plotly)
})
})
```

# Introduction

This package collects tools for reporting open data about
Bioconductor assets and distribution activities.

# Support site usage

```{r do1}
library(BiocReporting)
get_support_site_stats()
```

# Download statistics

Relative to previous reports, this is more fine-grained.

```{r lkdl}
pls = summarize_software_downloads()
pls$ipplot
```

```{r lkdl2}
ggplotly(pls$dlplot)
```

# Commit statistics

Users can summarize commit activity for a GitHub user or organization.

```{r comstat, eval=FALSE}
## select only certain repositories for analysis
slugs <- c(
    "vjcitn/TxRegInfra2",
    "vjcitn/BiocOncoTK",
    "vjcitn/YESCDS",
    "vjcitn/xenLite"
)
## generates the necessary repository metadata
select_repositories(repo_slugs = slugs)

## summarize overall activity for an account and
## additional repositories
## gitcreds::gitcreds_set()
summarize_commit_activity(
    org = "waldronlab",
    addtl_repos = slugs,
    topics = "u24ca289073",
    start_date = "2023-08-31",
    end_date = "2024-09-01"
)
```

# LLM summary

Generate a summary of commit logs using a language model.

```{r llm, eval=FALSE}
commits <- c(
    "Initial commit of project alpha",
    "Added new feature",
    "Fixed bug with new feature"
)
llm_summary(commits)
```

# ORCID table

Obtain employment data from ORCID.

```{r orcid, eval=FALSE}
orcid_table(
    orcid_ids = c(
        "0000-0002-3242-0582",
        "0000-0003-4046-0063",
        "0000-0003-2725-0694"
    )
)
```